---
title: "lterdatasampler"
format: html
execute: 
  echo: false
---

```{r}
library(tidyverse)
library(lterdatasampler)
library(kableExtra)
```

# This figure shows the size distribution of fiddler crabs at various latitudes
```{r, fig.cap= "this is my caption"}
pie_crab <- pie_crab

ggplot(data = pie_crab, aes(x= latitude, y= size)) +
  geom_jitter() +
  theme_classic()
```

```{r}
crab_sum <- pie_crab %>% 
  group_by(site) %>% 
  summarise(mean_size = round(mean(size), 2),
            sd_size = round(sd(size), 2),
            sample_size = n())
```

# The table shows the mean size, standard deviation, and sample size of fiddler crabs by sites. Data from lterdatasampler package

```{r}
#| echo: false
crab_sum %>%
  kable(col.names = c("Site", "Mean Size", "Size Standard Deviation", "Sample Size")) %>%
  kable_classic() %>%
  scroll_box(height = "200px", width = "700px")
```

Johnson, D. 2019. Fiddler crab body size in salt marshes from Florida to Massachusetts, USA at PIE and VCR LTER and NOAA NERR sites during summer 2016. ver 1. Environmental Data Initiative. https://doi.org/10.6073/pasta/4c27d2e778d3325d3830a5142e3839bb (Accessed 2021-05-27).
Johnson DS, Crowley C, Longmire K, Nelson J, Williams B, Wittyngham S. The fiddler crab, Minuca pugnax, follows Bergmann’s rule. Ecol Evol. 2019;00:1–9. https://doi.org/10.1002/ece3.5883